Review Paper Draft

### 2020-06-29 main.tex
3.3 - 3.5: edits, explicit intercept term

\pb{Seems like we should explicitly include an intercept in all these models?}

To describe and compare PC-Lasso and LMM-Lasso, we consider an $n \times p$ matrix of genotype data $\boldsymbol{G}$ for $n$ subjects and $p$ SNPs, where each $G_{i,j} \in \{ 0, 1, 2 \}$ enumerates the number of allele copies subject $i$ has for SNP $j$. We denote the standardized version of this genotype matrix as $\bX$, where each $X_{ij} = (G_{ij} - 2 p_j) / \sqrt{p_j (1 - p_j)}$ and $p_j$ is the observed minor allele frequency (MAF) of SNP $j$. We assume that an $n \times 1$ vector of continuous phenotype values, $\by$, can be expressed as the sum of additive SNP effects, environmental confounding, and observational noise and consider the linear mixed model,
\begin{equation}
    \label{eqn:model}
    \by = \bX\bbeta + \bZ\bgamma + \beps
\end{equation}
where $\bbeta$ is a $p \times 1$ vector of SNP effects, $\bgamma$ is a $q \times 1$ vector of environmental effects, $\bZ$ is an $n \times q$ matrix that allocates environmental effects, and $\beps \sim N(\boldsymbol{0}, \sigmaee \bI_n)$. Often it is assumed that subjects belong to $q \le p$ subpopulations, and $\bZ$ is a corresponding incidence matrix of 0s and 1s. However, as we will discuss, this is not the only possibility.

Both PC-Lasso and LMM-Lasso rely on matrix decompositions of $\bX$ and realized relationship matrix (RRM), $\bK$, which describes the pair-wise genetic similarity among subjects \cite{hayes2009increased}. Using the singular value decomposition (SVD) of the standardized genotype matrix, we can derive the spectral decomposition of the RRM:

\begin{align}
    \label{eqn:k}
    \bK &= \frac{1}{p} \bX \bX^T \nonumber \\
                   &= \frac{1}{p} \bU \bD^2 \bU^T \nonumber \\
                   &= \frac{1}{p} \bU \bD (\bU \bD)^T \nonumber \\
                   &\propto \bR \bR^T,
\end{align}
where the columns of $\bU$ are the principal components of $\bX$ (equivalently, those of $\bK$) and $\boldsymbol{D}^2$ is a diagonal matrix of the singular values of $\bK$. The columns of $\boldsymbol{R}$ are therefore proportional to the principal components weighted by their corresponding singular values.

%------------------------------%
\subsection{PC-Lasso}
PC-Lasso uses the first $k$ principal components of $\bX$ to approximate $\bZ\bgamma$ and includes them in the model as unpenalized covariates. It has been shown \cite{hoffman2013correcting} that this corresponds to the regression model
\begin{equation}
    \label{eqn:pca_reg}
    \by = \bX\bbeta + \bU_{1:k}\boldsymbol{\alpha} + \beps 
\end{equation}
where $\bU_{1:k}$ is the $n \times k$ matrix of principal component vectors, $\boldsymbol{\alpha}$ their corresponding $k \times 1$ coefficient vector, and all other parameters are as defined in equation \eqref{eqn:model}. In a penalized regression framework, this model yields the objective function
\begin{equation}
    \label{eqn:pca_obj}
    Q(\boldsymbol{\beta, \alpha| X, y}) = \frac{1}{2n} ||\boldsymbol{y} - \boldsymbol{X \beta} - \bU_{1:k}\boldsymbol{\alpha}||_2^2 + \lambda || \boldsymbol{\beta} ||_1
\end{equation}
where $\lambda$ is a tuning parameter, and $|| \boldsymbol{\beta} ||_1 = \sum_{j=1}^p |\beta_j|$ denotes the $\ell_1$ norm of the regression coefficients, and $||.||_2$ the $\ell_2$ norm. Note that the principal component regression coefficients, $\boldsymbol{\alpha}$, are not included in the penalty term. Modeling unobserved confounding using fixed effects in this manner thus requires the estimation of $p + k + 1$ parameters.

%------------------------------%
\subsection{LMM-Lasso}
LMM-Lasso models $\bZ\bgamma$ as a random effect assuming 
$$\bgamma \sim N\left(\boldsymbol{0}, \frac{\sigmagg}{p} \bI_p \right).$$  Typically, $\bZ$ is not observed directly, and a common convention is to assume $\bZ = \bX$ \cite{wang2018multiplex, lippert2011fast, yang2014advantages}. Then, rather than assuming anything about $\bgamma$ directly, let $\bu=\bX\bgamma$ represent the random effect and assume $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigmagg \bK)$. This results in the LMM regression model
\begin{equation}
    \label{eqn:lmm_reg}
    \by = \bX\bbeta + \bX\bgamma+ \beps,
\end{equation}
where we assume $\beps \independent \bX\bgamma$ and thus $\by  \sim N(\bX \bbeta, \bV)$, where $\bV = \sigmagg \textbf{K} + \sigmaee \textbf{I}$. LMM-Lasso then performs a weighted rotation of the original data, left-multiplying by $\bV^{-1/2}$ in a manner akin to generalized least squares to diagonalize the error term such that
\begin{equation}
\bV^{-\frac{1}{2}}\by \sim N(\bV^{-\frac{1}{2}}\bX \bbeta, \bI).
\end{equation}
\anna{...however, as Karl Rohe paper shows, GLS does not completely translate to penalized regression...comment on this?}
Using the spectral decomposition of $\bK$ described in equation \eqref{eqn:k}, we can gain further insight into the mechanism of this transformation. Note that $\bV^{-1}$ can be expressed using the following matrix factorization \anna{PROVIDED U IS N X N... see Lippert 2011 for details about the dimensions and contents of U} 
\begin{align*}
    \bV^{-1} &= (\sigmagg \bK + \sigmaee \bI)^{-1}\\
    &=(\sigmagg \bU \bD^2 \bU^T + \sigmaee \bU \bU^T)^{-1}\\
    &= (\bU (\sigmagg \bD^2 + \sigmaee \bI) \bU^T)^{-1}\\
    &=\bU (\sigmagg \bD^2 + \sigmaee \bI)^{-1} \bU^T.
\end{align*}
By incorporating these decompositions, the transformed data can be expressed as $\bW \bXT$ and $\bW \byT$, respectively, where $\bXT = \bU^T \bX$, $\byT = \bU^T \by$, and $\bW = \text{diag}\{w_1, ... w_n\}$ where $w_i$ corresponds to the square root of the $i$th element of the diagonal matrix $(\sigmagg \boldsymbol{D}^2 + \sigmaee \bI)^{-1}$. Together, this yields the objective function
\begin{equation}
\label{eqn:lmm_obj}
Q(\bbeta | \bXT, \byT, \bW) = || \bW (\byT - \bXT \bbeta)||_2^2 + \lambda || \bbeta ||_1.
\end{equation}
An advantage to modeling unobserved confounding using a random effect, as opposed to fixed effects as in PC-Lasso, is that this requires the estimation of substantially fewer parameters: $p + 2$ for LMM-Lasso-Rakitsch, and $p + 3$ for LMM-Lasso-ggmix.

@@

\pb{talk about both their similarities AND their differences.}

Despite the apparent dissimilarities between PC-Lasso and LMM-Lasso, it has been shown that the random effect formulation of model \eqref{eqn:model} used by LMM-Lasso can be equivalently expressed in terms of fixed effects. \cite{zhang2015principal} derived this equivalence using a probabilistic PCA formulation, while \cite{hoffman2013correcting} used the singular value decomposition of $\bX$, and the decomposition of $\bK$ shown in equation \eqref{eqn:k}.

@@

In carrying out simulation studies of the LMM regression model \eqref{eqn:lmm_reg}, a common practice \citep{Rakitsch2012, bhatnagar2019simultaneous} is to draw a new value of the quantity $\bX\bgamma$ from a $N(\boldsymbol{0}, \sigmagg \bK)$ for each replication of the analysis.  We argue that this is somewhat misleading from the perspective of understanding the statistical properties of the method. Averaging over situations in which the environmental confounding is constantly changing direction and magnitude ``washes out'' bias in $\hat{\bbeta}$ while inflating the variance. To see why this is the case, consider the OLS \pb{have to define OLS somewhere, if it's not already defined} estimates of $\hat{\bbeta}$ based on model \eqref{eqn:lmm_reg}:
\begin{align*}
    \mathbb{E}(\hat{\bbeta}) &= (\bX^T \bX)^{-1} \bX^T \mathbb{E}(\by)\\
    &=  (\bX^T \bX)^{-1} \bX^T \mathbb{E}(\bX\bbeta + \bX\bgamma + \beps)\\
    &\quad\\
    \mathbb{V}(\hat{\bbeta}) &= (\bX^T \bX)^{-1} \bX^T \mathbb{V}(\by)\\
    &=  (\bX^T \bX)^{-1} \bX^T \mathbb{V}(\bX\bbeta + \bX\bgamma + \beps)\\
    &=  (\bX^T \bX)^{-1} \bX^T \mathbb{V}(\bX\bgamma + \beps) \bX  (\bX^T \bX)^{-1}.
\end{align*}
Under the assumption that $\bgamma \sim N(\boldsymbol{0}, \frac{\sigmagg}{p} \bI_p)$, $\mathbb{E}(\hat{\bbeta}) = \bbeta, \mathbb{V}(\hat{\bbeta}) = \frac{\sigmagg}{p}\bI + \sigmaee (\bX^T \bX)^{-1}$ \pb{this is not a sentence}. To return to our earlier example involving confounding due to air quality, randomly drawing a new value of $\bX\bgamma$ for each replication would mean that subpopulation A may be exposed to good air quality in one replication, and bad air quality in the next. Reporting the average across these situations is inconsistent with the question we are truly interested in, namely: what would happen if we took repeated samples from fixed populations A and B? Those repeated samples would show a systematic bias due to the difference in air quality, but this is masked if we generate new values of $\bX\bgamma$ with each replication. Considering $\bgamma$ as a fixed quantity is more consistent with the usual meaning of environmental confounding. Specifically, in the low-dimensional OLS setting, under the assumption that the quantity $\bgamma$ is fixed, $\mathbb{E}(\hat{\bbeta}) = \bbeta + \bgamma, \mathbb{V}(\hat{\bbeta}) = \sigmaee (\bX^T \bX)^{-1}$.

Although we derive these quantities under model \eqref{eqn:lmm_reg}, where $\bZ = \bX$, these results also hold for the more general model \eqref{eqn:model}, where $\bZ \ne \bX$, by decomposing $\bZ \bgamma$ into components in and orthogonal to the column space of $\bX$. Assume \pb{NO ASSUMPTION IS NECESSARY HERE!} $\exists \boldsymbol{\tau, \psi}: \bZ \bgamma = \bX \boldsymbol{\tau + \psi}$ where $\boldsymbol{P}_{\bX} = \bX (\bX^T \bX)^{-1} \bX^T$, $\boldsymbol{\tau} \in \mathcal{C}(\boldsymbol{P}_{\bX})$, and $\boldsymbol{\psi} \in \mathcal{N}(\boldsymbol{P}_{\bX})$ \pb{need to say projection matrix, null space, column space}. Then,
\begin{align*}
    \by &= \bX\bbeta + \bZ\bgamma + \beps\\
    &= \bX\bbeta + \bX \boldsymbol{\tau} + \boldsymbol{\psi} + \beps\\
    &=  \bX \bbeta' + \beps'
\end{align*}
where $\boldsymbol{\tau}$ quantifies bias in the estimated $\boldsymbol{\hat{\beta}'}$ and $\boldsymbol{\psi}$ is absorbed by the error term. In other words, any model specified in terms of $\bZ$ and $\bgamma$ is equivalent to a parameterization using $\bX$ and $\boldsymbol{\tau}$.

\pb{should this paragraph move to next section?}
\anna{yes} Thus, given the nature of environmental confounding in our setting of interest, and in order to assess these methodological performance in terms of estimation accuracy, we simulate according to a fixed $\bgamma$ framework and using the following data-generating model
\begin{equation}
    \label{eqn:sim}
    \by = a \bX \bbeta + b \bZ \bgamma + c \beps,
\end{equation}
where $\by$ represents the phenotype, and $a, b, c$ are scaling factors determined such that the variance of $\by$ is equal to 1, and is partitioned into signal, environmental confounding, and random noise components,
\begin{equation}
    \label{eqn:parition_y}
    \mathbb{V}(\by) = \eta + (1 - \eta) \xi + (1-\eta)(1-\xi).
\end{equation}
Here, $\eta$ is the proportion of the variance of $\by$ attributable to genetic factors, commonly referred to as the narrow-sense heritability, and $\xi$ partitions the remaining variance of $\by$ into latent environmental heterogeneity and random noise. \pb{So, for example, $\eta=0.5$ and $\xi=0.7$ means that\ldots} Given our modeling objective of accurately estimating the effect sizes of observed SNPs, $\eta$ also represents our data-generating model's signal to noise ratio (SNR).

@@

>>>>

To describe and compare PC-Lasso and LMM-Lasso, we consider an $n \times p$ matrix of genotype data $\boldsymbol{G}$ for $n$ subjects and $p$ SNPs, where each $G_{i,j} \in \{ 0, 1, 2 \}$ enumerates the number of allele copies subject $i$ has for SNP $j$. We denote the normalized version of this genotype matrix as $\bX$, where each $X_{ij} = (G_{ij} - 2 p_j) / \sqrt{p_j (1 - p_j)}$ and $p_j$ is the minor allele frequency (MAF) of SNP $j$ \cite{zhang2015principal, price2006principal}. We assume that an $n \times 1$ vector of continuous phenotype values, $\by$, can be expressed as the sum of additive SNP effects, environmental confounding, and observational noise and consider the linear mixed model,
\begin{equation}
    \label{eqn:model}
    \by = \Int + \bX\bbeta + \bZ\bgamma + \beps
\end{equation}
where $\Int$ is the intercept, $\bbeta$ is a $p \times 1$ vector of SNP effects, $\bgamma$ is a $q \times 1$ vector of environmental effects, $\bZ$ is an $n \times q$ matrix that allocates environmental effects, and $\beps \sim N(\boldsymbol{0}, \sigmaee \bI_n)$. Often it is assumed that subjects belong to $q \le p$ subpopulations, and $\bZ$ is a corresponding incidence matrix of 0s and 1s. However, as we will discuss, this is not the only possibility.

LMM-Lasso relies on matrix decompositions of $\bX$ and the realized relationship matrix (RRM), $\bK$, which describes the pair-wise genetic similarity among subjects \cite{hayes2009increased}. Using the singular value decomposition (SVD) of the normalized genotype matrix, we can derive the spectral decomposition of the RRM:

\begin{align}
    \label{eqn:k}
    \bK &= \frac{1}{p} \bX \bX^T \nonumber \\
                   &= \frac{1}{p} \bU \bD^2 \bU^T \nonumber \\
                   &= \frac{1}{p} \bU \bD (\bU \bD)^T \nonumber \\
                   &\propto \bR \bR^T,
\end{align}
where $\bD^2$ is an $n \times n$ diagonal matrix containing the $k$ nonzero eigenvalues of $\bK$ (equivalently, the $k$ nonzero squared singular values of $\bX$) on the top-left diagonal, followed by $n - k$ zeroes on the bottom-right diagonal, and $\bU$ is the corresponding $n \times n$ orthonormal matrix of the left eigenvectors of $\bK$ (equivalently, the left singular vectors of $\bX$.) The first $k$ columns of $\bU$ correspond to the nonzero eigenvalues of $\bK$ (squared singular values of $\bX$.) The columns of $\bR$ are therefore proportional to the principal components of $\bX$ or $\bK$.

%------------------------------%
\subsection{PC-Lasso}
PC-Lasso uses the first $k$ principal components of $\bX$ to approximate $\bZ\bgamma$ and includes them in the model as unpenalized covariates. It has been shown \cite{hoffman2013correcting} that this corresponds to the regression model
\begin{equation}
    \label{eqn:pca_reg}
    \by = \Int + \bX\bbeta + \bU_{1:k}\boldsymbol{\alpha} + \beps 
\end{equation}
where $\bU_{1:k}$ is the $n \times k$ matrix of principal component vectors, $\boldsymbol{\alpha}$ their corresponding $k \times 1$ coefficient vector, and all other parameters are as defined in equation \eqref{eqn:model}. In a penalized regression framework, this model yields the objective function
\begin{equation}
    \label{eqn:pca_obj}
    Q(\boldsymbol{\beta, \alpha| X, y}) = \frac{1}{2n} ||\by - \Int - \bX \bbeta- \bU_{1:k}\boldsymbol{\alpha}||_2^2 + \lambda || \bbeta ||_1
\end{equation}
where $\lambda$ is a tuning parameter, and $|| \boldsymbol{\beta} ||_1 = \sum_{j=1}^p |\beta_j|$ denotes the $\ell_1$ norm of the regression coefficients, and $||.||_2$ the $\ell_2$ norm. Note that the principal component regression coefficients, $\boldsymbol{\alpha}$, are not included in the penalty term. Modeling unobserved confounding using fixed effects in this manner thus requires the estimation of $p + k + 1$ parameters.

%------------------------------%
\subsection{LMM-Lasso}
LMM-Lasso models $\bZ\bgamma$ as a random effect assuming 
$$\bgamma \sim N\left(\boldsymbol{0}, \frac{\sigmagg}{p} \bI_p \right).$$  Typically, $\bZ$ is not observed directly, and a common convention is to assume $\bZ = \bX$ \cite{wang2018multiplex, lippert2011fast, yang2014advantages}. Then, rather than assuming anything about $\bgamma$ directly, let $\bu=\bX\bgamma$ represent the random effect and assume $\bu \sim N(\boldsymbol{0}, \sigmagg \bK)$. This results in the LMM regression model
\begin{equation}
    \label{eqn:lmm_reg}
    \by = \Int + \bX\bbeta + \bX\bgamma+ \beps,
\end{equation}
where we assume $\beps \independent \bX\bgamma$ and thus $\by  \sim N(\Int + \bX \bbeta, \bV)$, where $\bV = \sigmagg \textbf{K} + \sigmaee \textbf{I}$. LMM-Lasso performs a weighted rotation of the original data, left-multiplying by $\bV^{-1/2}$ in a manner akin to generalized least squares to diagonalize the error term such that
\begin{equation}
\bV^{-\frac{1}{2}}\by \sim N(\bV^{-\frac{1}{2}} \left(\Int +\bX \bbeta\right), \bI).
\end{equation}
\anna{...however, as Karl Rohe paper shows, GLS does not completely translate to penalized regression...comment on this?}
\begin{comment}
For ease of notation, we incorporate the intercept into the design matrix and let $\bX' = \begin{bmatrix} \textbf{1} & \bX \end{bmatrix}$ and $\bbeta' = \begin{pmatrix} \mu & \bbeta \end{pmatrix}^T$ so that we can express this more compactly as 
\begin{equation}
\bV^{-\frac{1}{2}}\by \sim N(\bV^{-\frac{1}{2}} \bX' \bbeta', \bI).
\end{equation}
\end{comment}
Using the spectral decomposition of $\bK$ described in equation \eqref{eqn:k}, we can gain further insight into the mechanism of this transformation. Note that $\bV^{-1}$ can be expressed using the following matrix factorization 
\begin{align*}
    \bV^{-1} &= (\sigmagg \bK + \sigmaee \bI)^{-1}\\
    &=(\sigmagg \bU \bD^2 \bU^T + \sigmaee \bU \bU^T)^{-1}\\
    &= (\bU (\sigmagg \bD^2 + \sigmaee \bI) \bU^T)^{-1}\\
    &=\bU (\sigmagg \bD^2 + \sigmaee \bI)^{-1} \bU^T.
\end{align*}
By incorporating these decompositions, the transformed data can be expressed as $\bW \bXT$ and $\bW \byT$, respectively, where $\bXT = \bU^T \bX$ and $\byT = \bU^T \left( \by - \Int \right)$, where we center $\by$ to simplify notation. $\bW = \text{diag}\{w_1, ... w_n\}$ where $w_i$ corresponds to the square root of the $i$th element of the diagonal matrix $(\sigmagg \boldsymbol{D}^2 + \sigmaee \bI)^{-1}$. Together, this yields the objective function
\begin{equation}
\label{eqn:lmm_obj}
Q(\bbeta' | \bXT, \byT, \bW) = || \bW (\byT - \bXT \bbeta)||_2^2 + \lambda || \bbeta ||_1.
\end{equation}
An advantage to modeling unobserved confounding using a random effect, as opposed to fixed effects as in PC-Lasso, is that this requires the estimation of substantially fewer parameters: $p + 2$ for LMM-Lasso-Rakitsch, and $p + 3$ for LMM-Lasso-ggmix.

@@

It has been shown that the random effect formulation of model \eqref{eqn:model} used by LMM-Lasso can be equivalently expressed in terms of fixed effects. \cite{zhang2015principal} derived this equivalence using a probabilistic PCA formulation, while \cite{hoffman2013correcting} used the singular value decomposition of $\bX$, and the decomposition of $\bK$ shown in equation \eqref{eqn:k}.

@@

In carrying out simulation studies of the LMM regression model \eqref{eqn:lmm_reg}, a common practice \citep{Rakitsch2012, bhatnagar2019simultaneous} is to draw a new value of the quantity $\bX\bgamma$ from a $N(\boldsymbol{0}, \sigmagg \bK)$ for each replication of the analysis.  We argue that this is somewhat misleading from the perspective of understanding the statistical properties of the method. Averaging over situations in which the environmental confounding is constantly changing direction and magnitude ``washes out'' bias in $\hat{\bbeta}$ while inflating the variance. To see why this is the case, consider the ordinary least squares (OLS) estimates of $\bbeta$ based on model \eqref{eqn:lmm_reg}: \anna{intercept stuff gets messy here - need to include}
\begin{align*}
    \mathbb{E}(\hat{\bbeta}) &= (\bX^T \bX)^{-1} \bX^T \mathbb{E}(\by)\\
    &=  (\bX^T \bX)^{-1} \bX^T \mathbb{E}(\bX\bbeta + \bX\bgamma + \beps)\\
    &\quad\\
    \mathbb{V}(\hat{\bbeta}) &= (\bX^T \bX)^{-1} \bX^T \mathbb{V}(\by)\\
    &=  (\bX^T \bX)^{-1} \bX^T \mathbb{V}(\bX\bbeta + \bX\bgamma + \beps)\\
    &=  (\bX^T \bX)^{-1} \bX^T \mathbb{V}(\bX\bgamma + \beps) \bX  (\bX^T \bX)^{-1}.
\end{align*}
Under the assumption that $\bgamma \sim N(\boldsymbol{0}, \frac{\sigmagg}{p} \bI_p)$, $\mathbb{E}(\hat{\bbeta}) = \bbeta, \mathbb{V}(\hat{\bbeta}) = \frac{\sigmagg}{p}\bI + \sigmaee (\bX^T \bX)^{-1}$ \pb{this is not a sentence}. To return to our earlier example involving confounding due to air quality, randomly drawing a new value of $\bX\bgamma$ for each replication would mean that subpopulation A may be exposed to good air quality in one replication, and bad air quality in the next. Reporting the average across these situations is inconsistent with the question we are truly interested in, namely: what would happen if we took repeated samples from fixed populations A and B? Those repeated samples would show a systematic bias due to the difference in air quality, but this is masked if we generate new values of $\bX\bgamma$ with each replication. Considering $\bgamma$ as a fixed quantity is more consistent with the usual meaning of environmental confounding. Specifically, in the low-dimensional OLS setting, under the assumption that the quantity $\bgamma$ is fixed, $\mathbb{E}(\hat{\bbeta}) = \bbeta + \bgamma, \mathbb{V}(\hat{\bbeta}) = \sigmaee (\bX^T \bX)^{-1}$.

Although we derive these quantities under model \eqref{eqn:lmm_reg}, where $\bZ = \bX$, these results also hold for the more general model \eqref{eqn:model}, where $\bZ \ne \bX$, by decomposing $\bZ \bgamma$ into components in and orthogonal to the column space of the projection matrix of $\bX$.

Define the projection matrix of $\bX$ by $\boldsymbol{P}_{\bX} = \bX (\bX^T \bX)^{-1} \bX^T$, and let $\mathcal{C}(\boldsymbol{P}_{\bX})$ and $\mathcal{N}(\boldsymbol{P}_{\bX})$ denote the column and null spaces of $\boldsymbol{P}_{\bX}$, respectively. $\exists \boldsymbol{\tau, \psi}: \bZ \bgamma = \bX \boldsymbol{\tau + \psi}$ , $\boldsymbol{\tau} \in \mathcal{C}(\boldsymbol{P}_{\bX})$, and $\boldsymbol{\psi} \in \mathcal{N}(\boldsymbol{P}_{\bX})$. Then,
\begin{align*}
    \by &= \bX\bbeta + \bZ\bgamma + \beps\\
    &= \bX\bbeta + \bX \boldsymbol{\tau} + \boldsymbol{\psi} + \beps\\
    &=  \bX \bbeta' + \beps'
\end{align*}
where $\boldsymbol{\tau}$ quantifies bias in the estimated $\boldsymbol{\hat{\beta}'}$ and $\boldsymbol{\psi}$ is absorbed by the error term. In other words, any model specified in terms of $\bZ$ and $\bgamma$ is equivalent to a parameterization using $\bX$ and $\boldsymbol{\tau}$.

@@

%------------------------------%
\subsection{Simulation study}
%------------------------------%

Given the nature of environmental confounding in our setting of interest, and in order to assess these methodological performance in terms of estimation accuracy, we simulate according to a fixed $\bgamma$ framework and using the following data-generating model
\begin{equation}
    \label{eqn:sim}
    \by = a \bX \bbeta + b \bZ \bgamma + c \beps,
\end{equation}
where $\by$ represents the phenotype, and $a, b, c$ are scaling factors determined such that the variance of $\by$ is equal to 1, and is partitioned into signal, environmental confounding, and random noise components,
\begin{equation}
    \label{eqn:parition_y}
    \mathbb{V}(\by) = \eta + (1 - \eta) \xi + (1-\eta)(1-\xi).
\end{equation}
Here, $\eta$ is the proportion of the variance of $\by$ attributable to genetic factors, commonly referred to as the narrow-sense heritability, and $\xi$ partitions the remaining variance of $\by$ into latent environmental heterogeneity and random noise. \pb{So, for example, $\eta=0.5$ and $\xi=0.7$ means that\ldots} Given our modeling objective of accurately estimating the effect sizes of observed SNPs, $\eta$ also represents our data-generating model's signal to noise ratio (SNR).
